Scale Space Edge Detection

### 2018-03-10 paper.tex
spelling

\section{Defining an Edge in Scale Space}
A useful thing to do when dealing with image features is to set up a coordinate system in terms of the local directional derivatives.
In this case, we do the same thing as the paper does and setup a coordinate system $(u,v)$ at any point $(x_0,y_0)$ on the image.
Here, the $v$-axis is parallel to the gradient direction at the point $(x_0, y_0)$, and the $u$-axis is perpendicular to the gradient direction at the same point. So then we define necessary angles as \cite{Lindeberg1998}
\begin{equation}
  \begin{pmatrix}
    \cos{\alpha} \\
    \sin{\alpha}
  \end{pmatrix}
  = \frac{1}{\sqrt{L_x^2+L_y^2}}
  \begin{pmatrix}
    L_x \\
    L_y
  \end{pmatrix}
  \Bigg|_{(x_0,y_0)}
\end{equation}
With our angles defined, we can then define our $(u,v)$ coordinate system by taking the respective partial derivatives of our spatial coordinate system
\begin{align}
  \partial_u &= \sin{\alpha}\; \partial_x - \cos{\alpha}\; \partial_y \\
  \partial_v &= \cos{\alpha}\; \partial_x + \sin{\alpha}\; \partial_y
\end{align}
So then we can define our partials of $L$ with respect to this new $(u,v)$ coordinate system. The results for $L_v$ can be found on page \pageref{t_v}. So then we define an edge in this coordinate system with the following conditions \cite{Lindeberg1998}
\begin{equation} \label{eq:c1}
  \begin{aligned}
    L_{vv} &= 0 \\
    L_{vvv} &< 0
  \end{aligned}
\end{equation}
The way we can then represent these conditions in terms of spatial derivatives is as follows \cite{Lindeberg1998}
\begin{equation}
  \begin{aligned}
    L_{vv} &= L_x^2L_{xx}+2L_xL_yL_{xy}+L_y^2L_{yy} = 0 \\
    L_{vvv} &= L_x^3L_{xxx} +3L_x^2L_yL_{xxy}+3L_xL_y^2L_{xyy}+L_y^3L_{yyy} < 0
  \end{aligned}
\end{equation}
The results for $L_{vv}$ can be found on page \pageref{t_vv}.
The results for $L_{vvv}$ can be found on page \pageref{t_vvv}.
This is useful for determining edges at a single scale, but if we are to determine edges over multiple scales, we must also develop an edge strength metric, $\varepsilon_{norm}L$.
Thus this adds two more conditions that must be satisfied for an edge to be classified in the scale space \cite{Lindeberg1998}
\begin{equation} \label{eq:c2}
  \begin{aligned}
    \partial_t(\varepsilon_{norm}L(x,y;t)) = 0\\
    \partial_{tt}(\varepsilon_{norm}L(x,y;t)) < 0
  \end{aligned}
\end{equation}
Then (Eq. \ref{eq:c1}) in conjunction with (Eq. \ref{eq:c2}) form the necessary constraints for us to define an edge in the scale space.
Now we must define what we mean by edge strength and give a clearer idea of $\varepsilon_{norm}$.

>>>>

\section{Defining an Edge in Scale Space}
A useful system to use when dealing with image features is to set up a coordinate system in terms of the local directional derivatives.
In this case, we do the same thing as the paper does and setup a coordinate system $(u,v)$ at any point $(x_0,y_0)$ on the image.
Here, the $v$-axis is parallel to the gradient direction at the point $(x_0, y_0)$, and the $u$-axis is perpendicular to the gradient direction at the same point. So then we define necessary angles as \cite{Lindeberg1998}
\begin{equation}
  \begin{pmatrix}
    \cos{\alpha} \\
    \sin{\alpha}
  \end{pmatrix}
  = \frac{1}{\sqrt{L_x^2+L_y^2}}
  \begin{pmatrix}
    L_x \\
    L_y
  \end{pmatrix}
  \Bigg|_{(x_0,y_0)}
\end{equation}
With our angles defined, we can then define our $(u,v)$ coordinate system by taking the respective partial derivatives of our spatial coordinate system
\begin{align}
  \partial_u &= \sin{\alpha}\; \partial_x - \cos{\alpha}\; \partial_y \\
  \partial_v &= \cos{\alpha}\; \partial_x + \sin{\alpha}\; \partial_y
\end{align}
So then we can define our partials of $L$ with respect to this new $(u,v)$ coordinate system. The results for $L_v$ can be found on page \pageref{t_v}. So then we define an edge in this coordinate system with the following conditions \cite{Lindeberg1998}
\begin{equation} \label{eq:c1}
  \begin{aligned}
    L_{vv} &= 0 \\
    L_{vvv} &< 0
  \end{aligned}
\end{equation}
The way we can then represent these conditions in terms of spatial derivatives is as follows \cite{Lindeberg1998}
\begin{equation}
  \begin{aligned}
    L_{vv} &= L_x^2L_{xx}+2L_xL_yL_{xy}+L_y^2L_{yy} = 0 \\
    L_{vvv} &= L_x^3L_{xxx} +3L_x^2L_yL_{xxy}+3L_xL_y^2L_{xyy}+L_y^3L_{yyy} < 0
  \end{aligned}
\end{equation}
The results for $L_{vv}$ can be found on page \pageref{t_vv}.
The results for $L_{vvv}$ can be found on page \pageref{t_vvv}.
This is useful for determining edges at a single scale, but if we are to determine edges over multiple scales, we must also develop an edge strength metric, $\varepsilon_{norm}L$.
Thus this adds two more conditions that must be satisfied for an edge to be classified in the scale space \cite{Lindeberg1998}
\begin{equation} \label{eq:c2}
  \begin{aligned}
    \partial_t(\varepsilon_{norm}L(x,y;t)) = 0\\
    \partial_{tt}(\varepsilon_{norm}L(x,y;t)) < 0
  \end{aligned}
\end{equation}
Then (Eq. \ref{eq:c1}) in conjunction with (Eq. \ref{eq:c2}) form the necessary constraints for us to define an edge in the scale space.
Now we must define what we mean by edge strength and give a clearer idea of $\varepsilon_{norm}$.
